---
title: "Session B - How do I make inferential statistics?."
author: <INSERT YOUR NAME>
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Throughout remember we will need tidyverse. Additionally we will continue to work with the MASS package and the cats data. Go ahead and load this in.

```{r Exercise0, message=FALSE}
library(tidyverse)
library(MASS)
data("cats")
```

-------------

When we conduct inferential statistics, we are simply formulating the same types of questions that we were asking in descriptive statistics but checking this in a more mathematically rigorous manner. For example in order to see whether there is a difference in body weights between the male and female cats we can conduct a t-test. Have a look at the following t-test for the body weights.

```{r T-TestBody}
cats_male <- cats %>%
  filter(Sex == 'M')

cats_female <- cats %>%
  filter(Sex == 'F')

t.test(cats_male$Bwt, cats_female$Bwt)
```

### Exercise 1

Is there a difference between the mean heart weight of the male and female cats? Conduct a t-test in order to check this.
[Hint: you do not need to recreate the dataframes cats_male and cats_female]

```{r T-TestHeart}

```

-------------

Did you notice that the R programme automatically performed the Welch t-test? Why might this be a good thing from what we have learnt?

### Exercise 2

Re-perform the t-test using the two sample t-test. To do this you may need to look at the parameters of the t-test function using ?t.test. Compare the confidence intervals of the two different tests, which one is more conservative? What can we take away about the difference in mean weights?

```{r T-TestHeart2}

```

-------------

### Exercise 3

Formally write out the hypothesis of the tests above, including a rigourous statistical conclusion.

-------------

We did all this on the assumption that the mean of the data was normally distributed.

### Exercise 4

Which mathematical theorem allows us to do this? Write this down.

## Further Reading

[Common statistical tests are linear models (or: how to teach stats). By Jonas Kristoffer Lindeløv (blog, profile).](https://lindeloev.github.io/tests-as-linear/).

[Delacre, M., Lakens, D., & Leys, C. (2017). Why psychologists should by default use Welch's t-test instead of Student's t-test. International Review of Social Psychology, 30(1), 92-101.](https://research.tue.nl/en/publications/why-psychologists-should-by-default-use-welchs-t-test-instead-of-)

[Shatz, I. (2024). Assumption-checking rather than (just) testing: The importance of visualization and effect size in statistical diagnostics. Behavior Research Methods, 56(2), 826-845.](https://link.springer.com/article/10.3758/s13428-023-02072-x)
